A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-11 doc/popl2013/example.tex
speel cheeking
fixed caption typo

%This function also demonstrates the benefit of being able to dynamically
%(re-)discover disjointness.  Safely running both instances of 
%{\tt calc\_new\_currents} in parallel depends on knowing that {\tt rw0} and
%{\tt rw1} in {\tt execute\_time\_steps} are disjoint.  Similarly, parallel
%execution of the instances of {\tt update\_voltage} requires knowing that
%{\tt rn0} is disjoint from {\tt rn1}.  In both cases, this knowledge was
%statically available in {\tt simulate\_circuit} and could have been captured
%in a region relationship, but it would have resulted in much more complicated
%code.
%Instead, an inexpensive dynamic disjointness check is performed by the Legion
%runtime, and the safety of parallel execution follows from the soundness of
%the type system.
The {\tt execute\_time\_steps} function also demonstrates the benefit of dynamically
being able to discover disjointness.  To run the two intances of 
{\tt calc\_new\_currents} in parallel requires knowing that {\tt rw0}
and {\tt rw1} are disjoint.  There is a similar requirement for parallel
execution of the two {\tt update\_voltage} calls with {\tt rn0} and {\tt rn1}.  In
both cases, this knowledge was statically available in {\tt simulate\_circuit}
and could have been captured in a region relationship at the cost
of much more complicated code.  Instead, an inexpensive dynamic disjointness
check by the Legion runtime will discover the parallelism.

@@

\begin{lstlisting}[float={t},label={lst:circuit_leaf},caption={Circuilt Leaf Functions}]
function calc_new_currents[rl,rw,rn,rg] ( ptr_list : wire_list<rl,rw,rn,rg>@rl ), 
      reads(rl,rw,rn,rg), writes(rw) : bool =
  if isnull(ptr_list) then true else
  let wire_node : wire_list<rl,rw,rn,rg> = read(ptr_list) in
  let wire : CircuitWire<rn,rg> = read(wire_node.1) in
  let in_node : CircuitNode = read(wire.1) in
  let out_node : CircuitNode = read(wire.2) in
  let current : float = (in_node.1 - out_node.1) /  wire.3 in 
  let new_wire : CircuitWire<rn,rg> = <wire.1,wire.2,wire.3,current> in
  let _ : CircuitWire<rn,rg>@rw = write(wire_node.1, new_wire) in
      calc_new_currents[rl,rw,rn,rg](wire_node.2)

>>>>

%This function also demonstrates the benefit of being able to dynamically
%(re-)discover disjointness.  Safely running both instances of 
%{\tt calc\_new\_currents} in parallel depends on knowing that {\tt rw0} and
%{\tt rw1} in {\tt execute\_time\_steps} are disjoint.  Similarly, parallel
%execution of the instances of {\tt update\_voltage} requires knowing that
%{\tt rn0} is disjoint from {\tt rn1}.  In both cases, this knowledge was
%statically available in {\tt simulate\_circuit} and could have been captured
%in a region relationship, but it would have resulted in much more complicated
%code.
%Instead, an inexpensive dynamic disjointness check is performed by the Legion
%runtime, and the safety of parallel execution follows from the soundness of
%the type system.
The {\tt execute\_time\_steps} function also demonstrates the benefit of dynamically
being able to discover disjointness.  To run the two instances of 
{\tt calc\_new\_currents} in parallel requires knowing that {\tt rw0}
and {\tt rw1} are disjoint.  There is a similar requirement for parallel
execution of the two {\tt update\_voltage} calls with {\tt rn0} and {\tt rn1}.  In
both cases, this knowledge was statically available in {\tt simulate\_circuit}
and could have been captured in a region relationship at the cost
of much more complicated code.  Instead, an inexpensive dynamic disjointness
check by the Legion runtime will discover the parallelism.

@@

\begin{lstlisting}[float={t},label={lst:circuit_leaf},caption={Circuit Leaf Functions}]
function calc_new_currents[rl,rw,rn,rg] ( ptr_list : wire_list<rl,rw,rn,rg>@rl ), 
      reads(rl,rw,rn,rg), writes(rw) : bool =
  if isnull(ptr_list) then true else
  let wire_node : wire_list<rl,rw,rn,rg> = read(ptr_list) in
  let wire : CircuitWire<rn,rg> = read(wire_node.1) in
  let in_node : CircuitNode = read(wire.1) in
  let out_node : CircuitNode = read(wire.2) in
  let current : float = (in_node.1 - out_node.1) /  wire.3 in 
  let new_wire : CircuitWire<rn,rg> = <wire.1,wire.2,wire.3,current> in
  let _ : CircuitWire<rn,rg>@rw = write(wire_node.1, new_wire) in
      calc_new_currents[rl,rw,rn,rg](wire_node.2)
